A comparison of different methods for calculating tangent-stiffness matrices in a massively parallel computational peridynamics code.

### 2014-04-18 jacobian_calc_CMAME.tex
recolored mesh figures

\begin{figure}[tbp] \centering \includegraphics[width=0.7\textwidth]{./figs/mesh2000.png}
\caption{2000 node mesh} \label{fig:SCMesh}
\end{figure}

@@

\begin{figure}[tbp] \centering \includegraphics[width=0.7\textwidth]{./figs/mesh1000000.png}
\caption{1000000 node mesh} \label{fig:MCMesh}
\end{figure}

>>>>

\begin{figure}[tbp] \centering \includegraphics[width=1.0\textwidth]{./figs/mesh2000_replacement.png}
\caption{2000 node mesh} \label{fig:SCMesh}
\end{figure}

@@

\begin{figure}[tbp] \centering \includegraphics[width=1.0\textwidth]{./figs/mesh1000000_replacement.png}
\caption{1000000 node mesh} \label{fig:MCMesh}
\end{figure}
